### 2019-10-28 inst/README.rmd
roxygenize

- Have you ever written a long script in R that conducts lots of
  analyses and wished that someone would come along and make it all
  clearer to understand and use?
- Well you’re not alone. 
- A recent survey of over 1500 scientists reported a crisis of
  reproducibility with "selective reporting" being the most cited
  contributing factor and 80% saying code availability is playing a
  role.
- [Rclean](https://github.com/ProvTools/Rclean) was created to help
  scientists more *easily* write "cleaner" code by providing a simple,
  rigorous way to isolate the minimal code you need in order to
  produce a specific result (e.g. object, plot, output written to
  disk).
- [Rclean](https://github.com/ProvTools/Rclean) is built on data
  provenance, a formal representation of a computation, and uses graph
  analysis to determine the minimal path from inputs to results.
- The goal is to help facilitate code transparency, reproducibility,
  reusability and ultimately help scientists spend more time on
  research and less time on software.

@@

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ProvTools/Rclean")
```

@@

@@

```{r eval = TRUE}
clean("example/simple_script.R")
```

This returns a list of possible results detected in the script,
including execution lines (not counting lines with no code or that are
commented). We can now pick the result we want to focus on for
cleaning:

```{r eval = TRUE}
clean("./example/simple_script.R", "tab.15")
```

This produces the minimal code detected from the script. It also
detects library dependencies and inserts them into the code (`libs =
TRUE`).

It can be handy just to take a look at the isolated code, but you can
save the code for later use or sharing (e.g. creating a reproducible
example for getting help) with the `write.code` function:

```{r eval = FALSE}
my.code <- clean("example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

If you would like to copy your code to your clipboard, you can do that
by not specifying a file path. You can now paste as needed to create a
simpler script.

```{r eval = FALSE}
write.code(my.code)
```

Retrospective Provenance
========================

So far, we've been using "prospective" provenance generated from the
static code prior to execution. *Rclean* can also be used with
"retrospective" provenance, which is recorded during execution of a
script. Using it facilitates more accurate code cleaning, We can pass
the provenance to the `clean` function via `options`:

```{r eval = TRUE}
options(prov.json = readLines("example/prov_micro.json"))
```

Now that we have the provenance loaded, we can start
cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
list of possible values we can get code for, notice that the option
*rp* (i.e. "retrospective provenance") has been set to `TRUE`:

```{r eval = TRUE}
clean(file = "example/micro.R", rp = TRUE)
```

Similar to before, you can then pick and choose from among these
results and get the essential code to produce the output, like so:

```{r eval = TRUE}
clean(file = "example/micro.R", var = "x", rp = TRUE)
```

Happy cleaning!

>>>>

- [Rclean](https://github.com/ProvTools/Rclean) was created to help
  scientists more *easily* write "cleaner" code. 
- Written with research scientists that are results oriented in mind,
  the package's primary function provides a simple way to isolate the
  minimal code you need to produce a specific result, such as a
  statistical table or a figure.
- By focusing on specific results, large and/or complicated analytical
  scripts can be paired down to the essentials and easily re-factored
  to be more robust and easily shared.

@@

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("MKLau/Rclean")
```

@@

```{r eval = TRUE, echo = FALSE results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")

```

@@

```{r eval = FALSE} 
script <- "example/simple_script.R"

```

Here's a quick look at the code:

```{r eval = TRUE}
readLines(script)

```

You can get a list of the variables found in an object with
`get_vars`.

```{r eval = TRUE}
get_vars(script)

```

Sometimes for more complicated scripts, it can be helpful to see a
 network graph showing the interdependencies of
 variables. `code_graph` will produce a network diagram showing which
 lines of code produce which variables (e.g. 1 -> "out"):

```{r eval = TRUE}
code_graph(script)
```

Now, we can now pick the result we want to focus on for cleaning:

```{r eval = TRUE}
clean(script, "tab.15")
```

We can also select several variables at the same time:

```{r eval = TRUE}
my.vars <- c("tab.12", "tab.15")
clean(script, my.vars)
```

While just taking a look at the simplified code can be very helpful,
you can also save the code for later use or sharing (e.g. creating a
reproducible example for getting help) with `keep`:

```{r eval = FALSE}
my.code <- clean(script, my.vars)
keep(my.code, file = "results_tables.R")
```

If you would like to copy your code to your clipboard, you can do that
by not specifying a file path. You can now paste the simplified as needed.

```{r eval = FALSE}
keep(my.code)
```
